\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage[margin=0.65in]{geometry}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}
\raggedright
\setlength{\tabcolsep}{0in}
\setlength{\parindent}{0pt}
\emergencystretch=2em

\titleformat{\section}
  {\vspace{-4pt}\scshape\raggedright\large\bfseries}
  {}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

\pdfgentounicode=1

% -------------------------
% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1}}
\newcommand{\resumeSubheading}[4]{
  \item
  \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textbf{\small #2} \\
    \textit{\small #3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-6pt}
}
\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \small #1 & \textbf{\small #2} \\
  \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in,label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.18in,label=\textbullet,itemsep=2pt,topsep=2pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}}

\begin{document}

% ---------- HEADING ----------
\begin{center}
    {\Large \scshape Anson Chan} \\[2mm]
    \footnotesize
    \faPhone\ (604) 889-2211 \quad
    \faEnvelope\ ananryry180@gmail.com \quad
    \faLinkedin\ \href{https://www.linkedin.com/in/ansonnchan/}{linkedin.com/in/ansonnchan} \quad
    \faGithub\ \href{https://github.com/ansonnchan}{github.com/ansonnchan}
\end{center}

% ----------- EDUCATION -----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{University of British Columbia}{Expected Graduation: May 2028}
{Bachelor of Applied Science, Computer Engineering}{Vancouver, BC}
\resumeItemListStart
\resumeItem{Relevant Coursework: Software Construction I, Computing Systems I/II, Data Structures and Algorithms, Numerical Approximation and Discretization, Probability}
\resumeItem{Co-op Availability: 16 months beginning May 2026}
\resumeItemListEnd
\resumeSubHeadingListEnd

% ----------- WORK EXPERIENCE -----------
\section{Work Experience}
\resumeSubHeadingListStart
\resumeSubheading
{Borrow'd}{January 2026 -- April 2026}
{Backend Software Engineer Intern}{Remote}
\resumeItemListStart
\resumeItem{Triaged and resolved backend issues in a \textbf{Django} codebase, fixing production-impacting bugs to improve platform stability.}
\resumeItem{Strengthened \textbf{PostgreSQL} data integrity by correcting relational constraint violations and refining state-validation logic.}
\resumeItem{Wrote and expanded \textbf{Django} unit tests for critical backend paths, reducing regression risk in production releases.}
\resumeItem{Collaborated with QA and maintainers to convert bug reports into merged \textbf{GitHub PRs}, improving fix-to-deployment velocity.}
\resumeItemListEnd
\resumeSubHeadingListEnd

% ----------- PROJECTS -----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{MyInternship} $|$ \emph{\href{https://internship-tracker-frontend-nu.vercel.app/}{Website} $|$ \href{https://github.com/ansonnchan/MyInternship}{GitHub}}}
{Java $|$ Spring Boot $|$ Next.js $|$ TypeScript $|$ PostgreSQL}
\resumeItemListStart
\resumeItem{Built and deployed a full-stack internship tracker that lets users manage applications in one dashboard.}
\resumeItem{Developed a \textbf{Spring Boot REST API} with \textbf{PostgreSQL} to support secure, user-specific \textbf{CRUD} operations.}
\resumeItem{Implemented email classification logic that converts email content into structured status updates, reducing manual tracking effort.}
\resumeItem{Built a \textbf{TypeScript} + \textbf{Next.js} frontend with \textbf{JWT} authentication and resolved CORS/auth issues during \textbf{Render} and \textbf{Vercel} deployment.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{FindMyDesk UBC} $|$ \emph{\href{https://github.com/ansonnchan/FindMyDesk}{GitHub}}}
{Java $|$ Spring Boot $|$ REST API $|$ Google Maps API}
\resumeItemListStart
\resumeItem{Architected a recommendation engine in \textbf{Spring Boot}, delivering top-5 study spot suggestions based on user location.}
\resumeItem{Integrated the \textbf{Google Maps API} to compute distances and visualize locations through a custom web interface.}
\resumeItem{Designed \textbf{RESTful} backend endpoints to support scalable client-server data retrieval.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{WikiMediatorServer} $|$ \emph{\href{https://github.com/ansonnchan/WikiMediatorServer}{GitHub}}}
{Java $|$ Concurrency $|$ JUnit $|$ Gradle}
\resumeItemListStart
\resumeItem{Engineered a thread-safe \textbf{Java} server to process concurrent multi-client query requests correctly.}
\resumeItem{Designed and implemented a thread-safe \textbf{LRU cache}, reducing redundant external requests and improving response latency.}
\resumeItem{Developed and executed \textbf{60+ JUnit tests}, automated with \textbf{Gradle}, to validate correctness under concurrent workloads.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{RateGuard API} $|$ \emph{\href{https://github.com/ansonnchan/rateguard-api}{GitHub}}}
{Python $|$ FastAPI $|$ PostgreSQL $|$ Redis $|$ Docker}
\resumeItemListStart
\resumeItem{Built an API protection service that enforces per-user and per-IP rate limits for backend reliability and abuse prevention.}
\resumeItem{Implemented Redis-based sliding-window throttling with standards-based \texttt{429} responses and retry metadata.}
\resumeItem{Added API key auth, request logging, and health checks to improve debuggability and cloud deployment readiness.}
\resumeItemListEnd

\resumeSubHeadingListEnd

% ----------- TECHNICAL SKILLS -----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\item \small{
\textbf{Languages:} Java, Python, TypeScript, JavaScript, SQL, C/C++ \\
\textbf{Backend/Infrastructure:} Spring Boot, FastAPI, Django, PostgreSQL, Redis, REST APIs, JWT, Docker \\
\textbf{Frontend:} Next.js, React, HTML/CSS \\
\textbf{Developer Tools:} Git/GitHub, VS Code, IntelliJ, AWS, Azure
}
\end{itemize}

\end{document}
